An ultra-low noise, high-voltage piezo driver

### 2016-11-06 referee_response.tex

\documentclass[12pt, oneside]{letter}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{amsmath}

\usepackage{siunitx}
\DeclareSIUnit{\sqrthz}{\ensuremath{\sqrt{\text{\hertz}}}}

\begin{document}

Dear Editors:

We thank the referees for their review of our paper, and are pleased they found it suitable for publication.
We are also thankful for their thoughtful comments, which have allowed us to improve our manuscript considerably.
Please see below for a detailed summary of our changes and answers to the referees' comments and questions.
Italics indicate quotes from the referees.

\textbf{1.}
\textit{There is only one missing piece in the analysis of this circuit-the phase of the transfer function. 
When designing feedback circuits the shape of the transfer function is of great importance, but so is the relative phase of the feedback. 
This is especially true in circuits involving digital components. 
In this manuscript I do not see any mention or analysis of the phase of transfer function. 
To complete this study a mention of the behavior of the circuit of the demonstration of the unloaded is needed.}

We completely agree, and it was an oversight to neglect this.
We have updated Fig.~7 to include the unloaded phase response.
We have also updated the figure caption to reflect this change.

\textbf{2.}
\textit{The section on Auxiliary design features [should be] made more concise by addressing the flexibility of the circuit design without going into the exact details implemented by the author. }

We agree that this section does not add to the novel design presented in the manuscript, and is better suited as supplemental material.
We have removed section II.D. (``Auxiliary design features'') and moved a few details we believe will be interesting to the reader from that section to a new paragraph at the end of section II.C. (``Digital control and slow modulation''), which reads ``The high-voltage design presented here has the flexibility to exist as a standalone circuit or be integrated with other electronics~\ldots~Of course many variations are possible, and we refer the reader to GitHub for more details on our specific implementation.''

\textbf{3.}
\textit{[I]t would be good to address how much current your circuit can provide, and compare that to typical currents needed for the different applications suggested in the introduction.}

We agree this would be useful, and have included an estimate of the current at the end of the first paragraph in Sec~II.
That sentence reads, ``The output current will be limited by the switching regulator and by the LM7171 op-amp used for low-noise stabilization (U2 in Fig.~1, which can supply at most $\approx\SI{100}{\milli\ampere}$), but is sufficient for nearly all piezoelectric applications.''

\textbf{4.}
\textit{You state that a high-voltage op-amp in a linear supply requires significant power.
That statement might raise some eyebrows, because often in a regulated supply the transistor that burns off excess voltage is physically separate from the op-amp, such that it's not the op-amp itself that's sinking the power. 
You might try rewording this just to avoid that critique.}

We have reworded this sentence (last sentence in paragraph 3 of the introduction): ``While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection, linear regulators must dissipate excess voltages as heat and so may be more cumbersome to deploy in the laboratory.''

\textbf{5.}
\textit{Maybe I missed this - but was the data in figure 6 used to make figure 5? If so, that should be stated.}

Fig. 5 was generated from an SR780 spectrum analyzer, while Fig. 6 was generated from a fast sampling ADC (PicoScope).
We have modified the first sentence of the Fig. 5 caption to make this more explicit.
It now reads ``Voltage noise power spectral density at various output voltages, as measured on an SR780 spectrum analyzer (color online).''

\textbf{6.}
\textit{The term "quench" circuit is a good description. But it is not called by that name in the datasheet, which made me a little confused when I looked for it in there. Also, you might want to state that this circuit performs the same function as a similar circuit suggested by the datasheet, but that this circuit was modified to fit your design (in other words, this is not exactly the same circuit suggested in the datasheet).}

We have modified the second sentence in the second-to-last paragraph of Sec.~II.C. (``Digital control and slow modulation'') to make this clearer.
Specifically, we have moved reference to the datasheet ``FET'' circuit to a footnote.
It now reads: ``\ldots To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit [FOOTNOTE: the quench circuit presented here is based on the pulldown FET discussed in the DRV2700 datasheet, with some additional modifications to suit our purposes.] to quickly shunt $\text{V}_\text{out}$ to ground (see Fig.~2).

\textbf{7.}
\textit{The noise model was very nice - and the agreement with measurement is surprisingly good! It is, however, something that most people implementing your design will only glance at. Mainly, we want to know what the noise is, and that it made sense to you, so that we know that there's not something you overlooked that could easily be changed to improve the circuit. As such, it might be nice to place this after you discuss measured results. Also, you compare the measured results to your model in this section, and it was a bit confusing because you hadn't talked about your measurements yet.}

\textit{Overall, the paper was a bit dense. You might want to go over it and consider what would make the paper more useful for people that want to implement your design. Most of them will want a basic understanding, but will probably trust your work and not want to take the time to reproduce calculations, etc. Try to explain things more concisely. When you describe how a part of the circuit works, you might want to have a paragraph explaining what a particular section does before giving details. I like that the paper is detailed, and it should be. But you might be able to help the reader with a little more refinement and organization.}

While we understand referee \#2's concern, this would require completely rewriting the paper to maintain a coherent flow. We think some of the confusion might arise from how the figures are placed in the draft (eg, results figures appearing side-by-side with the noise analysis figures). We have taken some care to re-format the figures so this is no longer true, which hopefully improves readability. We do try to motivate each section of the circuit heuristically before providing specific design details (eg, the caption to Fig.~1, last paragraph before Sec.~II.A, and the first sentences of each lettered subsection of Sec.~II.).

In an attempt to address this concern, however, we have made the following changes:

\begin{itemize}
\item End of the caption in Fig.~2 now includes, ``\ldots and details of this circuit are discussed in Sec.~II.C.'', and the figure itself is placed on an earlier page (closer to the full schematic). This leaves more room for the subsequent figures to be placed closer to where they are discussed.
\item Changed first sentence of the caption to Fig.~4 to read ``Modeled noise contributions (color online).'' to make this figure more distinct from figure from Fig.~5, which contains measured results.
\item Results figures (\#5-7) are placed more closely to the results section.
\item We modified the first two sentences of Sec.~III in an attempt to better motivate the subsequent discussion. They now read ``To better understand the circuit performance and the measured output noise reported in Sec.~IV, we introduce the noise model shown in Fig. 3. A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, and residual ripple from the DRV2700, all calculated at the node $\text{V}_\text{out}$) is shown in Fig.4, along with the cumulative root-mean-square (RMS) noise estimates in different frequency bands.''
\end{itemize}

We believe the noise analysis makes it clear how one could modify the circuit for different applications, and although it may get deep in the weeds, is an important part of the paper.
For those who want to implement our circuit directly, this section can be neglected and the schematic/layout downloaded from GitHub.
For those who want to make changes or improvements, this section is an orientation to the design considerations we made.

\textbf{8.}
\textit{There was very little discussion of other, similar work. Are there other papers that you need to cite?}

We have added the additional reference \#6 (doi:10.1063/1.3234261), and incorporated an additional sentence in the second paragraph of the introduction which reads, ``Other designs separate high- and low-voltage control pathways, which can extend the bandwidth to $\approx\si{\mega\hertz}$, but the low-voltage control is AC-coupled to the output.''

\textbf{9.}
\textit{Finally, it would be really good if you had something to compare to your circuit. For example, if you used the DRV2700 in the standard Boost + Amplifier mode (which is a much simpler build than your circuit), how does its noise and modulation bandwidth compare with your circuit? How does it's conversion efficiency compare? (does it draw more than the 150 mA of your design?) etc. }

We agree this would be nice for comparison, however we are not set up to easily perform this measurement.
However, we would like to point out that using DRV2700 boost/amplifier requires the piezo to be driven differentially, which may not be suitable in some instances.

With these changes, we believe the paper has been greatly improved.
Points 1 \& 2 address the provisional publication recommendations of reviewer \#1, while the remaining points incorporate comments from reviewer \#2.
We once again thank the referees and respectfully resubmit this paper to Review of Scientific Instruments.

Sincerely,

Neal Pisenti and Gretchen Campbell

\end{document}

### 2016-11-13 piezo.tex
Referee comments

Instrumentation electronics capable of supplying high voltages traditionally fall under one of two architectural umbrellas: DC-DC switching converters, and linear-type amplifiers.
While DC-DC converters are efficient and can work at very high voltages, they suffer from switching noise and limited control bandwidths.
Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high-voltage linear regulator or more typically from a secondary switching converter.
While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection\cite{PA84Datasheet}, linear regulators must dissipate excess voltages as heat and so may be more cumbersome to deploy in the laboratory.

We present a circuit with a hybrid architecture.
The high voltage is generated by a galvanically isolated DC-DC converter, while a low-noise, high-slew-rate op-amp simulatneously removes noise at the output and provides a low-gain, high-bandwidth ($\gtrsim \SI{100}{\kilo\hertz}$) modulation input for closed-loop feedback applications.
This architecture is able to achieve extremely low noise ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint PCB.
Additionally, the high-voltage output remains single-ended and referenced to ground, allowing it to drive piezo actuators with a grounded terminal.
The schematic is presented in Sec.~\ref{Sec:Circuit}, with a noise analysis in Sec.~\ref{Sec:NoiseAnalysis} and characteristic performance data in Sec.~\ref{Sec:Results}.
Complete design files, including the schematic, bill of materials, and board layout, can be found on GitHub.\cite{PiezoDesignFiles}
The board manufacture and component cost is less than \SI{200}[\$]{}, making it a cost-effective alternative to commercial options.

@@

The design principles discussed below show how we leverage the characteristics of a galvanically-isolated switching regulator without sacrificing the low-noise requirements of many laboratory applications.
Our design targets a \SI{250}{\volt} output, but we discuss straightforward modifications to the schematic that make it possible to tailor the gain and output range to a specific application.
The entire electronics package fits into a compact Eurocard rack module (with the high-voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.
The output current will be limited by the switching regulator and by the LM7171 op-amp used for low-noise stabilization (U2 in Fig.~\ref{Fig:PiezoCircuit}, which can supply at most $\approx\SI{100}{\milli\ampere}$\cite{LM7171Datasheet}), but is sufficient for nearly all piezoelectric applications.

Fig.~\ref{Fig:PiezoCircuit} shows an overview of the circuit schematic. 
A digital-to-analog converter (DAC) generates a voltage setpoint, $\text{V}_\text{ctl}$, which is sent to the high-voltage flyback regulator and to the low-noise stabilization circuit.
The flyback regulator (Sec.~\ref{Sec:DRV2700}) controls the potential between the high-voltage ($\text{V}_\text{HV}$) and floating-ground ($\text{V}_\text{FG}$) circuit nodes, while the low-noise stabilization circuitry (Sec.~\ref{Sec:LowNoiseStabilization}) controls the output node $\text{V}_\text{out}$ relative to the true circuit ground.
The DAC is controlled by an integrated microcontroller, and can be programmed to output slow ($\approx\SI{10}{\hertz}$) rail-to-rail voltage ramps in addition to setting the DC operating point (Sec.~\ref{Sec:SlowModulationMOS}).
To improve the large-amplitude slew rate, a MOSFET ``quench'' circuit (Fig.~\ref{Fig:MOS}) is included to reduce the $RC$ time constant of the high-voltage node $\text{V}_\text{out}$ when needed.
A low-pass filter with a switchable corner frequency can be engaged during DC operation to reduce $1/f$ noise from the DAC (discussed in Sec.~\ref{Sec:NoiseAnalysis}).
Fast output modulation between $\pm\SI{10}{\volt}$ can be achieved through the input node $\text{V}_\text{mod}$.
This node is DC-coupled to the high-voltage output, and is useful for closed-loop feedback control.

@@

The DRV2700 implements output voltage control by comparing the feedback input pin at node $\text{V}_\text{FB}$ with an internal \SI{1.3}{\volt} reference.
The resistors $R_9$ and $R_{10}$ are chosen such that pin FB is at \SI{1.3}{\volt} when the output of U1 is at ground: $R_{10}/(R_9+R_{10}) = \SI{1.3}{\volt}/\SI{5}{\volt} \approx \num{0.26}$.
The op-amp U1 subtracts $\text{V}_\text{FG}$ and $G\cdot \text{V}_\text{ctl}$ from the voltage at node $\text{V}_\text{HV}$, ensuring the DRV2700 regulates the output voltage such that
\begin{align}
\label{Eq:U1Output}
\text{V}_\text{HV} - \text{V}_{\text{FG}} &= G\cdot \text{V}_{\text{ctl}}\,,
\end{align}
where the gain $G$ is set by the resistor ratio $R_3/R_4 \equiv R_5/R_6$, and $\text{V}_\text{ctl}$ is the control voltage set by the DAC.
The capacitors $C_3$ and $C_4$ are chosen such that $C_3 = \SI{22}{\pico\farad}$ and
\begin{align}
\frac{C_4}{C_3} &= \frac{R_3}{R_4~||~R_7}\,,
\end{align}
as suggested by the DRV2700 datasheet\cite{DRV2700Datasheet}, where $R_6 = R_7 = R_8$, and $R_i~||~R_j \equiv R_i R_j/(R_i + R_j)$.
In our implementation, we choose a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6,7,8} = \SI{10}{\kilo\ohm}$), allowing a \SI{5}{\volt} control signal $\text{V}_\text{ctl}$ to span \SI{250}{\volt} at the output. 
A different DAC and/or a different gain factor could be chosen to adjust the maximum output voltage.\footnote{Note that the passive components must be rated for the chosen output voltage.}
The transformer (ATB3225, 1:10 step-up winding), diode, and RC feedback network are all based on values suggested in the DRV2700 datasheet.\cite{DRV2700Datasheet,DRV2700EVMUserGuide}

@@

%% place figure here for better text flow
\begin{figure}[t!]
\includegraphics[width=\columnwidth]{MOS}
\caption{MOSFET ``quench'' circuit.
When the mid-ground node $\text{V}_\text{MG}$ (also shown in Fig.~\ref{Fig:PiezoCircuit}) goes below the threshold value set at $\text{V}_\text{TH}$, the op-amp puts the HV MOSFET Q1 into conduction.
When engaged, the quench time constant is given by $\tau \approx R_\text{MOS} \text{C}_\text{out}$, which for our circuit is set to \SI{1}{\milli\second}. Capacitor $\text{C}_\text{out}=\SI{1}{\micro\farad}$ is shown in Fig.~\ref{Fig:PiezoCircuit}, and details of this circuit are discussed in Sec.~\ref{Sec:SlowModulationMOS}.
\label{Fig:MOS}}
\end{figure}

@@

The choice of component for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system. 
Because this resistive divider is responsible for accurately sensing the voltage $\text{V}_\text{out}$, noise introduced by these resistors cannot be corrected by the op-amp.
In general, resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $4 k_B T R$, where $T$ is the temperature and $k_B$ is Boltzmann's constant.\cite{Horowitz2015a:JN}
However, resistors also exhibit $1/f$ current noise caused by equilibrium fluctuations of the resistance.\cite{Clarke1974a,Voss1976a}
This excess noise depends on the applied voltage, and therefore is an important consideration in a high-voltage circuit.
It is also highly dependent on the resistor composition and varies from manufacturer to manufacturer.
Seifert, et. al.~\cite{Seifert2009a} characterized $1/f$ noise in a variety of resistors, and found that the Vishay TNPW \SI{0.1}{\percent}-series resistors showed a noise spectrum almost consistent with Johnson noise down to \SI{1}{\hertz}.
Our current design uses this series in a 1206 package, but we noticed low-frequency noise correlated with varying strain on the PCB, potentially due to the relatively large footprint of this package.
Future boards will instead use three TNPW \SI{0.1}{\percent} 0603 resistors in series for both R1 and R2 to minimize strain-induced output noise.

@@

As discussed below in Sec.~\ref{Sec:NoiseAnalysis}, without modification the DAC would dominate the noise performance of $\text{V}_\text{out}$.
Therefore, we add a single-pole low-pass filter between $\text{V}_\text{ctl}$ and the non-inverting node of U2 to bring the DAC noise contribution below other noise sources in the circuit.
This filter has a switchable corner frequency (between \SI{165}{\hertz} and \SI{0.8}{\hertz}) to optimize noise performance at DC while still permitting AC modulation when needed.
It consists of a \SI{20.5}{\kilo\ohm} resistor and \SI{47}{\nano\farad} capacitor, with a secondary \SI{10}{\micro\farad} capacitor that can be switched in to operate with the lower corner frequency.

@@

The high-voltage design presented here has the flexibility to exist as a standalone circuit or be integrated with other electronics, and we have included several auxiliary features to make this more convenient.
For example, the analog modulation input is differentially buffered to break ground loops, and the digital portion can be interfaced with other devices in the lab to expand conceivable control scenarios.
Secondary features include a divided-down output that can be used as a monitor or fed forward to a low-noise laser diode current controller like the one in Erickson, et. al.~\cite{Erickson2008a}
Of course many variations are possible, and we refer the reader to GitHub for more details on our specific implementation.\cite{PiezoDesignFiles}

@@

\begin{figure}[b]
\includegraphics[width=\columnwidth]{TimeDomain}
\caption{Time-domain traces of the high-voltage output (\SI{100}{\volt}, color online). (a) Short-time scatterplot (AC coupled).
The points have been down-sampled for clarity, and colored based on a normally-distributed probability of occurence in each 100-\si{\micro\second} timeslice (scaled to the most probable voltage).
The color thus provides a visual estimation of the RMS width.
(b) Long-term trace, measured on a Keithly~2010 digital multimeter. A~\SI{100}{\volt} DC offset is subtracted from the plotted values. The top panel shows the lab temperature during the same time period.\label{Fig:TimeDomain}}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{PiezoModulationTransfer}
\caption{Modulation input transfer function (color online). The solid blue line indicates the unloaded frequency response, with the phase plotted in the lower panel. The dash-dotted orange trace shows the response with a \SI{700}{\nano\farad} piezoelectric actuator~{(Thorlabs PN~AE0505D08F)}. Several mechanical resonances above $\approx\SI{50}{\kilo\hertz}$ are clearly visible. The dashed green trace shows the response under a \SI{1}{\micro\farad} capacitive load. Loaded response bandwidth is $\approx~\SI{100}{\kilo\hertz}$, while the unloaded bandwidth is $\approx~\SI{5}{\mega\hertz}$ as indicated by the black dashed lines marking the $\SI{45}{\degree}$ phase margin.\label{Fig:TransferFunc}}
\end{figure}

>>>>

Instrumentation electronics capable of supplying high voltages traditionally fall under one of two architectural umbrellas: DC-DC switching converters, and linear-type amplifiers.
While DC-DC converters are efficient and can work at very high voltages, they suffer from switching noise and limited control bandwidths.
Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high-voltage linear regulator or more typically from a secondary switching converter.
While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection\cite{PA84Datasheet}, linear regulators must handle any excess voltage by dissipating heat and so may be more cumbersome to deploy in the laboratory.

We present a circuit with a hybrid architecture.
The high voltage is generated by a galvanically isolated DC-DC converter, while a low-noise, high-slew-rate op-amp simultaneously removes noise at the output and provides a low-gain, high-bandwidth ($\gtrsim \SI{100}{\kilo\hertz}$) modulation input for closed-loop feedback applications.
This architecture is able to achieve extremely low noise ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint PCB.
Additionally, the high-voltage output remains single-ended and referenced to ground, allowing it to drive piezo actuators with a grounded terminal.
The schematic is presented in Sec.~\ref{Sec:Circuit}, with a noise analysis in Sec.~\ref{Sec:NoiseAnalysis} and characteristic performance data in Sec.~\ref{Sec:Results}.
Complete design files, including the schematic, bill of materials, and board layout, can be found on GitHub.\cite{PiezoDesignFiles}
The board manufacture and component cost is less than \SI{200}[\$]{}, making it a cost-effective alternative to commercial options.

@@

The design principles discussed below show how we leverage the characteristics of a galvanically-isolated switching regulator without sacrificing the low-noise requirements of many laboratory applications.
Our design targets a \SI{250}{\volt} output, but we discuss straightforward modifications to the schematic that make it possible to tailor the gain and output range to a specific application.
The entire electronics package fits into a compact Eurocard rack module (with the high-voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.
The high-voltage output current will be limited by the switching regulator and by the LM7171 op-amp used for low-noise stabilization (U2 in Fig.~\ref{Fig:PiezoCircuit}, which can supply at most $\approx\SI{100}{\milli\ampere}$\cite{LM7171Datasheet}), but is sufficient for nearly all piezoelectric applications.

Fig.~\ref{Fig:PiezoCircuit} shows an overview of the circuit schematic. 
A flyback regulator (Sec.~\ref{Sec:DRV2700}) controls the potential between the high-voltage ($\text{V}_\text{HV}$) and floating-ground ($\text{V}_\text{FG}$) circuit nodes, while the low-noise stabilization circuitry (Sec.~\ref{Sec:LowNoiseStabilization}) controls the output node $\text{V}_\text{out}$ relative to the true circuit ground.
A digital-to-analog converter (DAC) generates a voltage setpoint, $\text{V}_\text{ctl}$, which is sent to the high-voltage flyback regulator and to the low-noise stabilization circuit.
The DAC is controlled by an integrated microcontroller, and can be programmed to output slow ($\approx\SI{10}{\hertz}$) rail-to-rail voltage ramps in addition to setting the DC operating point (Sec.~\ref{Sec:SlowModulationMOS}).
To improve the large-amplitude slew rate, a MOSFET ``quench'' circuit (Fig.~\ref{Fig:MOS}) is included to reduce the $RC$ time constant of the high-voltage node $\text{V}_\text{out}$ when needed.
A low-pass filter with a switchable corner frequency can be engaged during DC operation to reduce $1/f$ noise from the DAC (discussed in Sec.~\ref{Sec:NoiseAnalysis}).
Fast output modulation between $\pm\SI{10}{\volt}$ can be achieved through the input node $\text{V}_\text{mod}$.
This node is DC-coupled to the high-voltage output, and is useful for closed-loop feedback control.

@@

The DRV2700 implements output voltage control by comparing the feedback input pin at node $\text{V}_\text{FB}$ with an internal (\SI{1.3}{\volt}) reference.
The resistors $R_9$ and $R_{10}$ are chosen such that pin FB is at \SI{1.3}{\volt} when the output of U1 is at ground: $R_{10}/(R_9+R_{10}) = \SI{1.3}{\volt}/\SI{5}{\volt} \approx \num{0.26}$.
The op-amp U1 subtracts $\text{V}_\text{FG}$ and $G\cdot \text{V}_\text{ctl}$ from the voltage at node $\text{V}_\text{HV}$, ensuring the DRV2700 regulates the output voltage such that
\begin{align}
\label{Eq:U1Output}
\text{V}_\text{HV} - \text{V}_{\text{FG}} &= G\cdot \text{V}_{\text{ctl}}\,,
\end{align}
where the gain $G$ is set by the resistor ratio $R_3/R_4 \equiv R_5/R_6$, and $\text{V}_\text{ctl}$ is the control voltage set by the DAC.
The capacitors $C_3$ and $C_4$ are chosen such that $C_3 = \SI{22}{\pico\farad}$ and
\begin{align}
\frac{C_4}{C_3} &= \frac{R_3}{R_4~||~R_7}\,,
\end{align}
as suggested by the DRV2700 datasheet\cite{DRV2700Datasheet}, where $R_6 = R_7 = R_8$, and $R_i~||~R_j \equiv R_i R_j/(R_i + R_j)$.
In our implementation, we choose a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6,7,8} = \SI{10}{\kilo\ohm}$), allowing a \SI{5}{\volt} control signal $\text{V}_\text{ctl}$ to span \SI{250}{\volt} at the output. 
A different DAC and/or a different gain factor could be chosen to adjust the maximum output voltage.\footnote{Note that the passive components must be rated for the chosen output voltage.}
The transformer (ATB3225, 1:10 step-up winding), diode, and RC feedback network are all based on values suggested in the DRV2700 datasheet.\cite{DRV2700Datasheet,DRV2700EVMUserGuide}

@@

%% place figure here for better text flow
\begin{figure}[t!]
\includegraphics[width=\columnwidth]{MOS}
\caption{MOSFET ``quench'' circuit.
When the mid-ground node $\text{V}_\text{MG}$ (also shown in Fig.~\ref{Fig:PiezoCircuit}) goes below the threshold value set at $\text{V}_\text{TH}$, the op-amp puts the HV MOSFET Q1 into conduction.
When engaged, the quench time constant is given by $\tau \approx R_\text{MOS} \text{C}_\text{out}$, which for our circuit is set to \SI{1}{\milli\second}. The capacitor $\text{C}_\text{out}=\SI{1}{\micro\farad}$ is shown in Fig.~\ref{Fig:PiezoCircuit}, and details of this circuit are discussed in Sec.~\ref{Sec:SlowModulationMOS}.
\label{Fig:MOS}}
\end{figure}

@@

The choice of components for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system.
Because this resistive divider is responsible for accurately sensing the voltage $\text{V}_\text{out}$, noise introduced by these resistors cannot be corrected by the op-amp.
In general, resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $4 k_B T R$, where $T$ is the temperature and $k_B$ is Boltzmann's constant.\cite{Horowitz2015a:JN}
However, resistors also exhibit $1/f$ current noise caused by equilibrium fluctuations of the resistance.\cite{Clarke1974a,Voss1976a}
This excess noise depends on the applied voltage, and therefore is an important consideration in a high-voltage circuit.
It is also highly dependent on the resistor composition and varies from manufacturer to manufacturer.
Seifert, et. al.~\cite{Seifert2009a} characterized $1/f$ noise in a variety of resistors, and found that the Vishay TNPW \SI{0.1}{\percent}-series resistors showed a noise spectrum almost consistent with Johnson noise down to \SI{1}{\hertz}.
Our current design uses this series in a 1206 package, but we noticed low-frequency noise correlated with varying strain on the PCB, potentially due to the relatively large footprint of this package.
Future boards will instead use three TNPW \SI{0.1}{\percent} 0603 resistors in series for both R1 and R2 to minimize strain-induced output noise.

@@

As discussed below in Sec.~\ref{Sec:NoiseAnalysis}, without modification the DAC would dominate the noise performance of $\text{V}_\text{out}$.
Therefore we add a single-pole, low-pass filter between $\text{V}_\text{ctl}$ and the non-inverting node of U2 to bring the DAC noise contribution below other noise sources in the circuit.
This filter has a switchable corner frequency (between \SI{165}{\hertz} and \SI{0.8}{\hertz}) to optimize noise performance at DC while still permitting AC modulation when needed.
It consists of a \SI{20.5}{\kilo\ohm} resistor and \SI{47}{\nano\farad} capacitor, with a secondary \SI{10}{\micro\farad} capacitor that can be switched in to operate with the lower corner frequency.

@@

The high-voltage design presented here has the flexibility to exist as a standalone circuit or be integrated with other electronics, and we have included several auxiliary features to make this more convenient.
For example, the analog modulation input is differentially buffered to break ground loops (not shown in Fig.~\ref{Fig:PiezoCircuit}), and the digital portion can be interfaced with other devices in the lab to expand conceivable control scenarios.
Secondary features include a divided-down output that can be used as a monitor or fed forward to a low-noise laser diode current controller like the one in Erickson, et. al.~\cite{Erickson2008a}
Of course many variations are possible, and we refer the reader to our GitHub page for more details on our specific implementation.\cite{PiezoDesignFiles}

@@

\begin{figure}[b]
\includegraphics[width=\columnwidth]{TimeDomain}
\caption{Time-domain traces of the high-voltage output (\SI{100}{\volt}, color online). (a) Short-time scatterplot, measured on a PicoScope~5442B (AC coupled).
The points have been down-sampled for clarity, and colored based on a normally-distributed probability of occurence in each 100-\si{\micro\second} timeslice (scaled to the most probable voltage).
The color thus provides a visual estimation of the RMS width.
(b) Long-term trace, measured on a Keithly~2010 digital multimeter. A~\SI{100}{\volt} DC offset is subtracted from the plotted values. The top panel shows the lab temperature during the same time period.\label{Fig:TimeDomain}}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{PiezoModulationTransfer}
\caption{Modulation input transfer function (color online). The solid blue line indicates the unloaded frequency response, with the phase plotted in the lower panel. The dash-dotted orange trace shows the response with a \SI{700}{\nano\farad} piezoelectric actuator~{(Thorlabs PN~AE0505D08F)}. Several mechanical resonances above $\approx\SI{50}{\kilo\hertz}$ are clearly visible. The dashed green trace shows the response under a \SI{1}{\micro\farad} capacitive load. Loaded response bandwidth is $\approx~\SI{100}{\kilo\hertz}$, and the unloaded gain is flat within $\SI{0.1}{\decibel}$ out to $\SI{1}{\mega\hertz}$ where the phase is \SI{-20}{\degree}.\label{Fig:TransferFunc}}
\end{figure}
